\huge \textbf{Parameter Forecasts From CMB Lensing and Galaxy Lensing Power- and Bispectra}

### 2025-04-05 paper/paper_draft.tex
paper changes

% !TEX root = /Users/jonasfrugte/Desktop/Research_Project/fisher_calc_weak_lensing/paper/paper.tex
\documentclass[11pt]{article} % Choose a document class, like 'article', 'report', or 'revtex4-2' for scientific papers

@@

\affil[1]{Independent Researcher, The Netherlands}
\affil[2]{Van Swinderen Institute for Particle Physics and Gravity, University of Groningen, Nijenborgh 4, 9747 AG Groningen, The Netherlands}
\affil[ ]{}
\affil[ ]{\textit{E-mail:} \texttt{jonasfrugte@gmail.com}}

\date{20 February 2025} % Removes the default date

\begin{document}
\begin{center}
    \textit{Please note:}\\ This is still a draft version of the paper I am planning to finish April 2025. It thus may still contain mistakes, missing citations, typo's, etc. that will not be present in the final version. The code used to write this paper can be found on my GitHub: \url{https://github.com/Jonas-Frugte/fisher_calc_weak_lensing}.
\end{center}
\pagebreak
\maketitle

% \textbf{
%     \huge \noindent 
%     Parameter Forecasts From CMB $\times$ Galaxy Lensing Powerspectra $\times$ Bispectra
%     \vspace{0.5cm}
%     \\
%     \normalsize
%     Jonas Frugte, Daan Meerburg\\
%     20 February 2025
%     }\\
% \vspace{0.5cm}
\hrule

\begin{abstract}
    Weak gravitational lensing of the Cosmic Microwave Background (CMB) and distant galaxies provides a powerful probe of the large-scale structure and cosmic expansion history. Upcoming Stage-IV surveys like the Simons Observatory, CMB-S4, LSST, and Euclid promise unprecedented precision, motivating detailed forecasts of their constraining power. While lensing power spectra are standard cosmological tools, non-Gaussianities induced by structure formation encode additional information in the bispectrum. In this work, we perform a comprehensive Fisher matrix forecast to quantify the detectability of these signals and the cosmological constraints achievable by combining power spectrum and bispectrum measurements from both CMB lensing and galaxy shear, including their cross-correlations. We model Stage-IV-like experimental specifications and forecast constraints on the standard $\Lambda$CDM parameters, the sum of neutrino masses ($\Sigma m_\nu$), and the dark energy equation of state ($w_0$). We demonstrate that incorporating bispectra significantly enhances constraints, reducing marginalized parameter uncertainties by up to $\sim \texttt{X}\%$ compared to power spectra alone. We project competitive constraints, including $\sigma(H_0) = \texttt{X.X~km/s/Mpc}$, $\sigma(\sigma_8) = \texttt{X.XXX}$, and $\sigma(\Sigma m_\nu) = \texttt{X.XX~eV}$.
    \end{abstract}
\pagebreak
%\tableofcontents

>>>>

% !TEX root = /Users/jonasfrugte/Desktop/Research_Project/fisher_calc_weak_lensing/paper/paper_draft.tex
\documentclass[11pt]{article} % Choose a document class, like 'article', 'report', or 'revtex4-2' for scientific papers

@@

\affil[1]{Independent Researcher, The Netherlands}
\affil[2]{Van Swinderen Institute for Particle Physics and Gravity, University of Groningen, Nijenborgh 4, 9747 AG Groningen, The Netherlands}
\affil[ ]{}
\affil[ ]{\textit{E-mail:} \texttt{jonasfrugte@gmail.com}}
 % Removes the default date

\begin{document}
\maketitle

% \textbf{
%     \huge \noindent 
%     Parameter Forecasts From CMB $\times$ Galaxy Lensing Powerspectra $\times$ Bispectra
%     \vspace{0.5cm}
%     \\
%     \normalsize
%     Jonas Frugte, Daan Meerburg\\
%     20 February 2025
%     }\\
% \vspace{0.5cm}

\begin{center}
    \textbf{NB: Currently still in draft.}
\end{center}
\hrule

\begin{abstract}
    % Weak gravitational lensing of the Cosmic Microwave Background (CMB) and distant galaxies provides a powerful probe of the large-scale structure and cosmic expansion history. Upcoming Stage-IV surveys like the Simons Observatory, CMB-S4, LSST, and Euclid promise unprecedented precision, motivating detailed forecasts of their constraining power. While lensing power spectra are standard cosmological tools, non-Gaussianities induced by structure formation encode additional information in the bispectrum. In this work, we perform a comprehensive Fisher matrix forecast to quantify the detectability of these signals and the cosmological constraints achievable by combining power spectrum and bispectrum measurements from both CMB lensing and galaxy shear, including their cross-correlations. We model Stage-IV-like experimental specifications and forecast constraints on the standard $\Lambda$CDM parameters, the sum of neutrino masses ($\Sigma m_\nu$), and the dark energy equation of state ($w_0$). We demonstrate that incorporating bispectra significantly enhances constraints, reducing marginalized parameter uncertainties by up to $\sim \texttt{X}\%$ compared to power spectra alone. We project competitive constraints, including $\sigma(H_0) = \texttt{X.X~km/s/Mpc}$, $\sigma(\sigma_8) = \texttt{X.XXX}$, and $\sigma(\Sigma m_\nu) = \texttt{X.XX~eV}$.
    \end{abstract}
\pagebreak
%\tableofcontents
